Viscous Erosion in Porous Media

### 2018-01-25 docs/methods/erosion_methods.tex
NM

Certain features of this shape can be predicted analytically by appealing to the principal of uniform stress distribution. In particular, consider the angle formed at the front and rear stagnation points. In long time, the stress becomes uniform, in particular in a small vicinity of this front angle in which body curvature can be ignored. Zooming in on the front angle, we can consider the problem of Stokes flow around an infinite wedge of opening angle $\oangle$. Exact solutions can be obtained to this problem via separation of variables in polar coordinates \cite{poz1997}. The corresponding stream function is $\psi = r^{\lambda}f(\theta)$, where $f$ satisfies the 4th order ODE
\begin{equation}
f'''' + 2(\lambda^2 - 2 \lambda + 2)f'' + \lambda^2(\lambda-2)^2 f = 0
\end{equation}
subject to boundary conditions. The corresponding shear stress evaluated on the surface of the wedge is $\tau = \mu r^{\lambda-2} f''(\alpha)$. Thus, the wedge of uniform stress corresponds to $\lambda = 2$. For this value, the general solution for $f$ is 
\begin{equation}
f(\theta) = B \sin(2\theta - \beta) + C \theta + D
\end{equation}
where $B, C$ are complex constants and $\beta$ is a real constant.

>>>>

Certain features of this shape can be predicted analytically by appealing to the principal of uniform stress distribution. In particular, consider the angle formed at the front and rear stagnation points. In long time, the stress becomes uniform, in particular in a small vicinity of this front angle in which body curvature can be ignored. Zooming in on the front angle, we can consider the problem of Stokes flow around an infinite wedge of opening angle $\oangle$. Exact solutions can be obtained to this problem via separation of variables in polar coordinates \cite{poz1997}. The corresponding stream function is $\psi = r^{\lambda}f(\theta)$, where $f$ satisfies the 4th order ODE
\begin{equation}
f'''' + 2(\lambda^2 - 2 \lambda + 2)f'' + \lambda^2(\lambda-2)^2 f = 0
\end{equation}
subject to boundary conditions $f(\alpha) = f'(\alpha) = 0$ and $f(0) = f''(0) = 0$.
The corresponding shear stress evaluated on the surface of the wedge is $\tau = \mu r^{\lambda-2} f''(\alpha)$. Thus, the wedge of uniform stress corresponds to $\lambda = 2$. For this value, the solution for $f$ that satisfies the appropriate symmetry across $\theta = 0$ is 
\begin{equation}
f(\theta) = B \sin (2 \theta) + C \theta
\end{equation}

%\begin{equation}
%f(\theta) = B \sin(2\theta - \beta) + C \theta + D
%\end{equation}
%where $B, C$ are complex constants and $\beta$ is a real constant.
